### 2015-04-16 motivation.tex
reword mixdown section.

\paragraph{Meta-build Systems}
{\it Meta-build systems} such as Contractor, WAF, and
MixDown~\cite{amundson:contractor,epperly+:mixdown,nagy:waf} are closely
related to package managers, but their focus is on ensuring that a single
{\it project} builds correctly along with all of its dependencies.  They do not address
larger, multi-user system administration issues such as versioning, naming
conventions, rapid multi-configuration installation, or maintaining many
divergent software stacks.

>>>>

\paragraph{Meta-build Systems}
{\it Meta-build systems} such as Contractor, WAF, and
MixDown~\cite{amundson:contractor,epperly+:mixdown,epperly+:mixdown-report,nagy:waf} are
related to package managers, but they focus on ensuring that a single
package builds correctly with its dependencies.  MixDown notably provides excellent
features for ensuring consistent compiler flags in a build.
However, these systems do not provide facilities to manage
large package repositories or combinatoric versioning.
